Artificial ecosystem selection reveals relationships between microbiome composition and ecosystem function

### 2022-04-08 Manuscript/manuscript.Rmd
update manuscript text

```{r initialize-packages}
library(tidyverse)
library(broom)
library(broman)
library(morris)
library(phyloseq)
library(ggpubr)
library(knitr)
library(corncob)
library(ggthemes)
library(microViz)
library(captioner)
figures <- captioner()
tables <- captioner(prefix = "Table")
```

@@

p <- plot_flux(fluxes, passage, log_ch4, ratio_log10, log10 = TRUE)

ggsave('fig1.jpg', p)

@@

p <- plot_herit(heritability)

ggsave('fig2.jpg', p)

@@

p <- plot_beta(ps)

ggsave('fig3.jpg', p)

write.table(fit_adonis, 'table_1.tsv')
# kable(col.names = c('Term', 'df', 'SS', 'R2', 'F', 'p'), 
#       digits = c(2,2,2,2,2,3),
## 	format = "Table",
## 	booktabs = T,
# 	caption = "PERMANOVA on Bray-Curtis and Jaccard dissimilarities.",
#   	label = "beta") %>%
#   pack_rows("Bray-Curtis", 1, 5) %>%
#   pack_rows("Jaccard", 6, 10)

@@

p <- dt_plot(dt_data)
ggsave('fig4.jpg', p)

@@

@@

@@

@@

@@

>>>>

```{r initialize-packages}
library(tidyverse)
library(broom)
library(broman)
library(morris)
library(phyloseq)
library(ggpubr)
library(knitr)
library(corncob)
library(ggthemes)
library(microViz)
library(captioner)
library(knitr)
library(kableExtra)
library(flextable)
figures <- captioner()
tables <- captioner(prefix = "Table")
```

@@

@@

@@

@@

@@

p <- plot_flux(fluxes, passage, log_ch4, ratio_log10, log10 = TRUE)
p
ggsave('fig1.jpg', p)

@@

p <- plot_herit(heritability)
p
ggsave('fig2.jpg', p)

@@

p <- plot_beta(ps)
p
ggsave('fig3.jpg', p)

@@

p <- dt_plot(dt_data)
p
ggsave('fig4.jpg', p)

@@

write.table(fit_adonis, 'table_1.tsv')
fit_adonis %>%
  mutate(metric = c(rep("aitchison", 5), rep("jaccard", 5))) %>% 
  select(metric, term:p.value) %>% 
	flextable()
# kable(col.names = c('Term', 'df', 'SS', 'R2', 'F', 'p'), 
#       digits = c(2,2,2,2,2,3),
## 	format = "Table",
## 	booktabs = T,
# 	caption = "PERMANOVA on Bray-Curtis and Jaccard dissimilarities.",
#   	label = "beta") %>%
#   pack_rows("Bray-Curtis", 1, 5) %>%
#   pack_rows("Jaccard", 6, 10)
